---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SpoTubeR

<!-- badges: start -->
<!-- badges: end -->

SpoTubeR is a package which combines data from the R wrappers spotifyr and tuber to match a given Spotify song with an associated YouTube music video. When given a Spotify Song or YouTube Music video, SpoTubeR generates a 'match score' equating to its confidence that the songs are a match. SpoTuber can also be used to explore compelling questions about how songs across different genres, by different artists, associated with different record labels, or released on different years may generate more or less popular music videos on YouTube in comparison with the song's popularity on Spotify.

## Installation

You can install the development version of SpoTubeR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Skotkin/SpoTubeR")
```

## Authentication
Users must create a Spotify API (only available on Premium accounts) and a YouTube API, then authenticate with the [auth_creds()] function, before they can use the other functions provided.

## SpoTubeR Function Example

This is a basic example of a SpoTubeR function and its output:

```{r example}
library(SpoTubeR)
library(knitr)
artist_comp('https://open.spotify.com/artist/6BRxQ8cD3eqnrVj6WKDok8?si=eS8ItlNFTtmtUOE5z5WwbA')
```

## License
Scripts are released under the MIT License
