---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpoTubeR)
library(knitr)
library(dplyr)
library(ggplot2)
library(tuber)
```

Learning to use R can be hard, and finding interesting data that can be used to create a variety of research questions can be even harder! We have created SpoTubeR as a package that can help people new to R and data science easily match Spotify songs with their existing YouTube music videos and compare their characteristics. Further, we provided functions which can help them to gather information about a song's genres, popularity, record labels, release years, and more. 

### Setting up Credentials/API

## First, create a Spotify and YouTube Client ID and insert your information with auth_creds()

```{r}
#auth_creds(spotify_id = "YOUR ID HERE", spotify_secret = "YOUR SECRET HERE", yt_key = "YOUR SECRET HERE")
```

Now that you have your Spotify and YouTube access tokens, you can start experimenting with SpoTubeR!


### Data: billboard100_apr26

To explore the basic functions inside of SpoTubeR, we'll use a dataset containing billboard's 100 most popular current songs on April 26th, 2026. 

```{r}
SpoTubeR::billboard100_apr26 |> View()
```

## Function Examples

Looking at the data set, I can see that the #1 artist on 4/26/26 was Ella Langley. I wonder how her music compares across platforms?

### Compare artists' content on Spotify and YouTube with artist_comp()
```{r}
# Inputting the spotify link (provided in the data set) to Ella Langley's top song into the function
SpoTubeR::artist_comp('https://open.spotify.com/artist/6BRxQ8cD3eqnrVj6WKDok8?si=7yliDpVUTXCUxKh_SuuPrw')[[2]] |> 
  kable(caption = "Ella Langley's music on Spotify vs YouTube", col.names = c("Song Title", "Spotify Popularity", "YouTube Views", "Match Confidence", "Spotify Popularity Rank", "YouTube Views Rank"))
```

After looking on Spotify, I can see that Ella Langley's is signed with Sony Music Nashville. I wonder what other musicians they have signed with?

### Compare a given label's popularity on Spotify with its popularity on YouTube with label_comp()

```{r}
# Using the Label Sony Music Nashville
SpoTubeR::label_comp('Sony Music Nashville')[[2]] |> 
  kable(caption = "Label's Top 5 Artist's Info", col.names = c("Song Title", "Spotify Popularity", "YouTube Views", "Match Confidence", "Spotify Popularity Rank", "YouTube Views Rank"))
```

Lets say I wanted to conduct my own analyses without using the top 100 data set

### Match Spotify songs to their artist's YouTube music video with match_spotify_song

```{r}
# Using Noah Kahn's Stick Season
SpoTubeR::match_spotify_song('https://open.spotify.com/track/0mflMxspEfB0VbI1kyLiAv?si=9c5d9964b777475d') |> 
  kable(caption = "Noah Kahn's Stick Season on Spotify vs YouTube", col.names = c("Spotify Popularity", "YouTube Views", "Match Confidence"))
```

How about the other way around?

### Match YouTube music videos to their artist's Spotify song with match_yt_song
```{r}
# Using Lady Gaga and Doechii's brand new song Runway
SpoTubeR::match_yt_song('https://www.youtube.com/watch?v=XXIX2WnfbpE') |> 
  kable(caption = "Lady Gaga and Doechii's Runway on YouTube vs Spotify", col.names = c("Spotify Popularity", "YouTube Views", "Match Confidence"))
```

## Visualizations with SpoTubeR

Finally, I want to compare the top 10/top 100 artists in our data set. 

WORK IN PROGRESS

# Most YouTube Views
```{r}
#top_10 <- billboard100_apr26 |> dplyr::filter(rank == 1:10) |> dplyr::select(spotify_link)

#for (i in 1:length(top_10)) {sapply(GET(top_10$spotify_link), SpoTubeR::artist_comp)}

# or apply(top_10, 1, SpoTubeR::artist_comp)
  
  #ggplot(aes(x = )) + geom_histogram() + coord_flip() + labs(title = "Distribution of YouTube Views for Billboard's Hot 100 songs on April 26th, 2026", x = "Song Titles", y = "Views")
```
