---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpoTubeR)
library(knitr)
library(dplyr)
library(ggplot2)
library(tuber)
```

Learning to use R can be hard, and finding interesting data that can be used to create a variety of research questions can be even harder! We have created SpoTubeR as a package that can help people new to R and data science easily match Spotify songs with their existing YouTube music videos and compare their characteristics. Further, we provided functions which can help them to gather information about a song's genres, popularity, record labels, release years, and more. 

### Setting up Credentials/API

## First, create a Spotify and YouTube Client ID and insert your information with auth_creds()

```{r}
#SpoTubeR::auth_creds(spotify_id = "YOUR ID HERE", spotify_secret = "YOUR SECRET HERE", yt_key = "YOUR SECRET HERE")
```

Now that you have your Spotify and YouTube access tokens, you can start experimenting with SpoTubeR!


### Data: billboard100_apr26

To explore the basic functions inside of SpoTubeR, we'll use a dataset containing billboard's 100 most popular current songs on April 26th, 2026. 

```{r}
SpoTubeR::billboard100_apr26 |>
  View()
```

## Function Examples

Looking at the data set, I can see that the #1 artist on 4/26/26 was Ella Langley. I wonder how her music compares across platforms?

### Compare artists' content on Spotify and YouTube with spotify_artist_comp()
```{r}
# Inputting the spotify link (provided in the data set) to Ella Langley's top song into the function
SpoTubeR::spotify_artist_comp('https://open.spotify.com/artist/6BRxQ8cD3eqnrVj6WKDok8?si=7yliDpVUTXCUxKh_SuuPrw')[[2]] |> 
  as.data.frame() |> 
  knitr::kable(caption = "Ella Langley's music on Spotify vs YouTube", col.names = c("Song Title", "Spotify Popularity", "YouTube Views", "Match Confidence", "Spotify Popularity Rank", "YouTube Views Rank"))
```

After looking on Spotify, I can see that Ella Langley's is signed with Sony Music Nashville. I wonder what other musicians they have signed with?

### Compare a given label's popularity on Spotify with its popularity on YouTube with label_comp()

```{r}
# Using the Label Sony Music Nashville
 Sony_Nash <- SpoTubeR::label_comp('Sony Music Nashville')

Sony_Nash_df <- data.frame(Artist = names(Sony_Nash))

for (i in 1:length(Sony_Nash)) {
  Sony_Nash_df$`Spotify Popularity`[i] <- Sony_Nash[[i]][[1]][[1]]
  Sony_Nash_df$`Spotify Follower Count`[i] <- Sony_Nash[[i]][[1]][[2]]
  Sony_Nash_df$`YouTube Subscriber Count`[i] <- Sony_Nash[[i]][[1]][[3]]
}

Sony_Nash_df |>
  knitr::kable(caption = "Label's Top 5 Artist's Info")
```

Lets say I wanted to conduct my own analyses without using the top 100 data set

### Match Spotify songs to their artist's YouTube music video with match_spotify_song

```{r}
# Using Noah Kahn's Stick Season
SpoTubeR::match_spotify_song('https://open.spotify.com/track/0mflMxspEfB0VbI1kyLiAv?si=9c5d9964b777475d') |>
  as.data.frame() |>
  knitr::kable(caption = "Noah Kahn's Stick Season on Spotify vs YouTube", col.names = c("Spotify Popularity", "YouTube Views", "Match Confidence"))
```

How about the other way around?

### Match YouTube music videos to their artist's Spotify song with match_yt_song
```{r}
# Using Lady Gaga and Doechii's brand new song Runway
SpoTubeR::match_yt_song('https://www.youtube.com/watch?v=XXIX2WnfbpE') |> 
  as.data.frame() |>
  knitr::kable(caption = "Lady Gaga and Doechii's Runway on YouTube vs Spotify", col.names = c("Spotify Popularity", "YouTube Views", "Match Confidence"))
```

## Visualizations with SpoTubeR

Finally, I want to compare the YouTube music video views and Spotify popularity score for the top 15 out of the top 100 artists in our data set. 

# Most YouTube Views
```{r}
top_15 <- billboard100_apr26 |>
  dplyr::filter(rank %in% 1:15) |>
  dplyr::select(spotify_link, track_name) |>
  mutate(views = NA, popularity = NA)

 for (i in 1:15) {
   base <- SpoTubeR::match_spotify_song(top_15$spotify_link[i])
   top_15$views[i] <- base[[2]]
   top_15$popularity[i] <- base[[1]]
   }

as.data.frame(top_15) |>
  ggplot2::ggplot(aes(x = views, y = popularity)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Distribution of YouTube Views and Spotify Popularity for Billboard's Hot \n 100 songs on April 26th, 2026", x = "YouTube Views", y = "Spotify Popularity Score") +
  geom_smooth(method = "lm") +
  annotate("label", x = 0.8, y = 50, size = 3, label = paste("Corr.", round(cor(top_15$views, top_15$popularity), 3)), color = "red", fontface = "bold")
```

As we can see that YouTube views and Spotify popularity scores have a positive correlation of 0.281. This makes sense because songs with greater Spotify popularity are expected to have more views on YouTube. However, it also makes sense that the correlation is not perfect since the Spotify popularity score is based on the song's popularity at a given point in time, while the YouTube view count is more of a measure of cumulative popularity over time (if a song is on YouTube for longer, it tends to have more views).
