---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpoTubeR)
library(knitr)
library(dplyr)
library(ggplot2)
library(tuber)
```

### Setting up Credentials/API

## Create a Spotify and YouTube Client ID and insert your information with auth_creds()

```{r}
#auth_creds(spotify_id = "YOUR ID HERE", spotify_secret = "YOUR SECRET HERE", yt_key = "YOUR SECRET HERE")
```

Now that you have your Spotify and YouTube access tokens, you can start experimenting with SpoTubeR!


### Data: billboard100_apr26

To explore the basic functions inside of SpoTubeR, we'll use a dataset containing billboard's 100 most popular current songs on April 26th, 2026. 

```{r}
SpoTubeR::billboard100_apr26 |> View()
```

## Function Examples

### Match Spotify songs to their artist's YouTube music video with match_spotify_song

```{r}
# Using the #1 song, Choosing Texas
SpoTubeR::match_spotify_song('https://open.spotify.com/track/65DbTqJKhbwqYbZ1Okr0rc?si=2c1b70f52fde43b7')

# Adding a Video Count Column to our Data Set
#billboard100_apr26 <- billboard100_apr26 |> 
  #mutate(temp_list = list(match_spotify_song(lapply(spotify_link, httr::GET))), YT_views = temp_list[[2]])
```

### Match YouTube music videos to their artist's Spotify song with match_yt_song
```{r}
# Using the #1 song, Choosing Texas
#SpoTubeR::match_yt_song('https://www.youtube.com/watch?v=nUsrYVxrDwI&list=RDnUsrYVxrDwI')
```


### Compare artists' content on Spotify and YouTube with artist_comp()
```{r}
# Using the #1 song, Choosing Texas
#SpoTubeR::artist_comp('https://open.spotify.com/track/65DbTqJKhbwqYbZ1Okr0rc?si=2c1b70f52fde43b7')
#or
#SpoTubeR::artist_comp('https://www.youtube.com/watch?v=nUsrYVxrDwI&list=RDnUsrYVxrDwI')
```

### Compare a given label's popularity on Spotify with its popularity on YouTube with label_comp()

```{r}
# Using the Label Universal
#SpoTubeR::label_comp('Universal')
```

## Creating Tables with SpoTubeR

```{r}
#SpoTubeR::billboard100_apr26 |> 
  #dplyr::select('track_name', 'artist_name', YT_views) |>
  #dplyr::group_by('track_name') |> 
  #dplyr::summarize('Song Name' = 'track_name', "Artist Name" = 'artist_name', "YT Popularity" = YT_views) |> kable()
```

## Visualizations with SpoTubeR

# Most YouTube Views
```{r}
#billboard100_apr26 |>
  #ggplot(aes(x = YT_views)) + geom_histogram() + coord_flip() + labs(title = "Distribution of YouTube Views for Billboard's Hot 100 songs on April 26th, 2026", x = "Song Titles", y = "Views")
```
